The GitHub Open Source Development Process \author{Kevin Peterson\\ Department of Information Technology\\ Clinical Informatics Support Systems\\ Mayo Clinic\\ 200 1st Street\\ Rochester, MN 55905\\ \small \texttt{peterson.kevin@mayo.edu} }

### 2013-03-29 paper/main.tex
Updated python code to only sample organization repositories.

\begin{abstract}
Open Source Software (OSS) has produced many successful projects. The development process by which these projects are produced is generally unstructured compared to commercial software -- but a definite pattern does arrive, and is no less a pattern. GitHub, a popular OSS code hosting website, and Git, the site's Source Code Management (SCM) tool of choice, may have the potential to fundamentally change ths process.

By analyzing a subset of GitHub repositories, this report will show how GitHub has influenced some very intrinsic aspects of traditional OSS development, such as developer hierarchies and issue close velocity. We find that many of the traditional aspects of OSS development remain, such most project development is done by a small group of core developers. Others assumptions about project hierarchy, such as a large number of Issue Reporters compared to Committers, seems unsupported by the data.
\end{abstract}

@@

A case study of the Apache Server project\cite{mockus2000case} shows that a dedicated community can produce software that rivals or exceeds commercial offerings. This study showed that even in the unstructured context of OSS, certain structures, hierarchies, and codes of conduct emerge. Contrast the Apache Server project to a successful project on GitHub. Although the spirit and intent may be the same, the tool set is drastially different. The intent of this work is to explore how GitHub facilitates this process, and also how it may cause it to evolve.

@@

In addition, three supporting research questions are proposed. These questions will draw upon data from this work, but also reference interviews with GitHub staff to better represent how GitHub may be changing how OSS development is conducted.

\subsection{Hypotheses}
The following hypotheses

@@

\subsection{Research Questions}

@@

\textit{Interview Q2: Many new Software Developers are will be starting their education/training already having experience with GitHub. How will Software Engineering as a discipline (and how it is taught) change to accodate the ideas popularized by GitHub?}\\

>>>>

\begin{abstract}
Open Source Software (OSS) projects, or software projects with publicly available source code, are realizing ever more important roles in both personal and business computing. As such, shifts in the way OSS is developed could have impacts on both the quantity and the quality of OSS projects.

The development process by which these projects are produced is generally unstructured compared to commercial software, but many projects do exhibit general development patterns. GitHub, a popular OSS code hosting website, along with Git, the site's Source Code Management (SCM) tool of choice, may have the potential to fundamentally change this process by facilitating new patterns and opportunities for developers.

By analyzing a subset of GitHub repositories, this report will show how GitHub has influenced some intrinsic aspects of traditional OSS development, such as developer hierarchies and issue close velocity. We find that many of the traditional aspects of OSS development remain, such as most project development is done by a small group of core developers. Other assumptions about project hierarchy, such as a large number of Issue Reporters compared to Committers, seems unsupported by the data.
\end{abstract}

@@

A case study of the Apache Server project\cite{mockus2000case} shows that a dedicated community can produce software that rivals or exceeds commercial offerings. This study showed that even in the unstructured context of OSS, certain structures, hierarchies, and codes of conduct emerge. Contrast the Apache Server project to a successful project on GitHub. Although the spirit and intent may be the same, the tool set is drastically different. The intent of this work is to explore how GitHub facilitates this process, and also how it may cause it to evolve.

@@

In addition, three supporting research questions are proposed. These questions will draw upon data from this work, but also reference interviews with GitHub staff to better represent how GitHub may be changing how OSS development is conducted. These qualitative observations, paired with the more qualitative data analysis, allows for a broad description of the way that GitHub is changing the Software Engineering landscape for OSS.

\subsection{Hypotheses}
The following hypotheses are presented in an effort to better understand the GitHub development process by analyzing data from actual GitHub projects. Each hypothesis will be backed by previous research in an attempt to show concrete ways in which the GitHub process may be changing the OSS development process. Where possible, results from previous research on the Apache Server[mockus2000case] is compared, as this work closely aligns with Hypothesis 2 and 3.

@@

\subsection{Research Questions}
To expand the analysis scope slightly, three qualitative research questions are posed. These, although backed by analyzed data where possible, are intended to show broader patterns, ideas, and motivations around the use of GitHub. Where possible, interviews\cite{begel2013social} where conducted to explore high level concepts and motivations.

@@

\textit{Interview Q2: Many new Software Developers are will be starting their education/training already having experience with GitHub. How will Software Engineering as a discipline (and how it is taught) change to accommodate the ideas popularized by GitHub?}\\
